### 2005-11-15 doc/EFA/efa.tex
*** empty log message ***

\subsection{Background}
\newpage
\section{Extended Finite Automaton (EFA)}
An Extended Deterministic Finite Automaton (EFA) is an
augmentation of a regular finite automaton. The regular automaton
$A$ is defined as $A=\langle Q,\Sigma,\delta, q_i,Q_m \rangle$.
Let $T=\{(q,\sigma)\in Q \times \Sigma: \delta(q,\sigma)!\}$
denote the set of transitions in the deterministic automaton $A$
and let $\tau_k$, $k=1,...,|T|$ denote the elements (transitions)
of $T$.

The automaton $A$ is extended by a set $X=X_1\times ... \times
X_n$, where $X_k$, $k=1,...,n$, are finite nonempty subsets of
$\mathbb{Z}$. The set $X$ is the domain of definition of an
$n$-tuple of integer variables $x=(x_1,...,x_n)$ with initial
value $x_0=(x_{10},...,x_{n0})$. We also add to $A$ an $|T|$-tuple
of function pairs $G=\big((g_{\tau_1},a_{\tau_1}),...,
(g_{\tau_{|T|}},a_{\tau_{|T|}})\big)$, where each pair
$(g_{\tau_k},a_{\tau_k})$ is associated to the corresponding
transition $\tau_k$ in $T$. $g_{\tau_k}$ is an evaluation of a
boolean formula (a guard formula) over $X$ i.e. $g_{\tau_k}:X
\rightarrow \{0,1\}$ saying if the corresponding transition
$\tau_k$ is enabled or not. $a_{\tau_k}$ is an updating (action)
function from $X$ to $X$ of the integer variables
$x=(x_1,...,x_n)$.

>>>>

\subsection{Background}
\newpage
\section{Finite Automaton (FA) with hierarchy}

\section{Extended Finite Automaton (EFA)}
The regular deterministic finite automaton $A$ is a $5$-tuple
\begin{eqnarray}
A=\langle Q,\Sigma,\delta, q_i,Q_m \rangle\nonumber
\end{eqnarray} where $Q$ is a finite set of states; $\Sigma$ (the alphabet) is a nonempty
set of events; $\delta$ is the transition function; $q_i$ is the
initial state and $Q_m \subseteq Q$ is the set of marked states.
An Extended Deterministic Finite Automaton (EFA) is an
augmentation of the regular finite automaton with guard and action
formulas associated to the transitions. The transitions in the EFA
are enabled if and only if a guard formula is true. Moreover, when
a transition in an EFA is taken, updating actions of a set of
finite integer variables may follow. Formally this is done as
follows.

Given a regular automaton $A=\langle Q,\Sigma,\delta, q_i,Q_m
\rangle$, let $T=\{(q,\sigma)\in Q \times \Sigma:
\delta(q,\sigma)!\}$ denote the set of transitions in $A$ and let
$\tau_k$, $k=1,...,|T|$ denote the elements (transitions) of $T$.
First, we add to $A$ a set $X=X_1\times ... \times X_n$, where
$X_k$, $k=1,...,n$, are finite nonempty subsets of $\mathbb{Z}$.
The set $X$ is the domain of definition of an $n$-tuple of integer
variables $x=(x_1,...,x_n)$ with initial value
$x_0=(x_{10},...,x_{n0})$. We also add to $A$ an $|T|$-tuple of
function pairs $G=\big((g_{\tau_1},a_{\tau_1}),...,
(g_{\tau_{|T|}},a_{\tau_{|T|}})\big)$, where each pair
$(g_{\tau_k},a_{\tau_k})$ is associated to the corresponding
transition $\tau_k$ in $T$. $g_{\tau_k}$ is an evaluation of a
boolean formula (a guard formula) over $X$ i.e. $g_{\tau_k}:X
\rightarrow \{0,1\}$ saying if the corresponding transition
$\tau_k$ is enabled or not. $a_{\tau_k}$ is an updating (action)
function from $X$ to $X$ of the integer variables
$x=(x_1,...,x_n)$.
